\TheTitle

### 2015-08-17 linvis.tex
Editing: Discussion

Our tool provides mechanisms and visualizations that other tools are unable to
produce. Continuous mining of the repository provides an additional dimension
to the dataset that would otherwise be lost, enabling us to reliably build
trees from the information we have.

@@

Our goal was to build a tool to enable maintainers to effectively navigate and
pull explanation of the changes performed to the kernel over a release.
Achieving this goal includes removing information that does not pertain to given
users. In figure \ref{fig:dag_view} and figure \ref{fig:tree_view}, we can
visually compare the results returned from gitk and our tool for the top-level
merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6'' from kernel version 3.10.
The relevant information in both of these figures is identical, but the
presentation durastically changes our understanding of what we are seeing.

This merge is relatively small, containing only four merges, three of which
only contain a single commit, and the last containing two commits. With our
tool, we are able to immediately see what commits and merges pertain to our
section of the kernel. The DAG view of this provides almost no explanation,
futhermore, users must work to determine where this merge ends and the next one
begins.

Our tool further enhances our understanding by immediately giving us the files
that were edited and the modules. We are able to determine that three files,
``palamas-regulator.c'' had two lines added and two lines removed,
``dbx500-prcmu.c'' had 12 lines added and 12 lines removed, and ``core.c'' had
5 lines added and 2 lines removed in the merge. Finally, we are able to
determine that only the module ``regulator'' was modified in this merge, and
there were 5 commits in the merge to this module.

\subsection{Performance Evaluation}

Re-structuring the kernel into a tree changes the runtime for the structures.
Originally, we were performing all of our tree-navigation using recursive SQL
queries. Recursive queries have terrible performance, with the average response
time from the database being around 3 seconds for a single operation. We found
that it was far more time-efficient to load an entire tree directly into
memory, then iterate over the objects returned to build the tree structures,
than it was to have the dbms perform the tree traversals, building the specific
trees for a commit. At this time, we have re-implemented the breadcrumbs, the
files, and the main tree to enhance the response times. We will discuss some We
will discuss the changes made.

The breadcrumbs are generated at response
time, so they must be generated quickly. We began with a single recursive SQL
query, but was unable get the results in the required time, causing all result
pages to render slowly. We replaced the recursive query with a single query
that would grab the entire merge tree, rooted at the top-level merge.

@@

This maintains the O(n) runtime for generating the breadcrumbs, while using an
iterative method for traversing the tree.

@@

\subsection{Extendability}
Due to how the asynchronous requests are performed, it is possible to query the
server for the tree and file information directly, allowing other users to
build their own front-ends for working with our tree-based system.

@@

The tree responses are generated as a single object. This object is the root
node of the tree, and may contain many objects with the same fields in the
``children'' field. The full response format for the tree looks like:

@@

The file responses contain only the files that the current merge or commit
works with. The response is a single object in the form of a tree. This object
is the root of the tree, and represents the current merge or commit. If the
current position in the tree is an inner node, the response will contain the
children in the ``children'' field, otherwise ``children'' will be null. The
full response format for the file response looks like:

>>>>

Our tool provides mechanisms and visualizations that other tools are unable to
produce. Continuous mining of the repository\cite{German} provides an
additional dimension to the dataset that would otherwise be lost, enabling us
to reliably build trees from the information we have.

@@

Our goal was to build a tool to enable maintainers to effectively navigate and
pull explanation of the changes performed to the kernel over the period of a
release.  Achieving this goal includes removing information that does not
pertain to given users. In figure \ref{fig:dag_view} and figure
\ref{fig:tree_view}, we can visually compare the results returned from gitk and
our tool for the top-level merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6''
from kernel version 3.10. The relevant information in both of these figures is
identical, but the presentation drastically changes our ability to comprehend
what we are seeing. The primary difference is the removal of irrelevant
information. In gitk (\ref{fig:dag_view}), the visualization results include
commits and merges from other components of the kernel, while our tool
(\ref{fig:tree_view}) only includes the results that are specific to the
component of the kernel that we are interested in.

This merge is relatively small, containing only four merges, three of which
only contain a single commit, and the last containing two commits. With our
tool, we are able to immediately see what commits and merges pertain to our
section of the kernel. The DAG view of this provides almost no explanation,
furthermore, users must work to determine where this merge ends and the next one
begins.

Our tool further enhances our understanding by immediately giving us the files
and modules that were edited. We are able to determine that three files,
``palamas-regulator.c'' had two lines added and two lines removed,
``dbx500-prcmu.c'' had 12 lines added and 12 lines removed, and ``core.c'' had
5 lines added and 2 lines removed. Finally, we are able to determine that only
the ``regulator'' module was modified in this merge and was modified by 5
commits.

\subsection{Performance Evaluation}
Originally, we were performing all of our tree-navigation, file information
gathering, and module information gathering using recursive SQL queries.
Recursive queries have terrible performance, with the average response time
from the database being around 3 seconds for a single operation. We found that
it was far more response time-efficient to load an entire merge tree directly
into memory, then iterate over the objects returned to build the tree
structures, than it was to have the dbms perform the tree traversals, building
the specific trees for a commit. At this time, we have re-implemented the
breadcrumbs, the files, and the main tree views to enhance the response times.
We will discuss some We will discuss the changes made.

The breadcrumbs are generated on page-load, so they must be generated quickly.
We began with a single recursive SQL query, but was unable get the results in
the desired time, causing all results pages to render slowly. We replaced the
recursive query with a single query that would grab the entire merge tree,
rooted at the top-level merge.

@@

This maintains the O(n) runtime for generating the breadcrumbs, while using an
iterative method for traversing the tree and dropping the response time from
around 3 seconds to at most 500ms.

@@

\subsection{Extendability}
Due to how the asynchronous requests are performed, it is possible to query the
server for the tree and file information directly, allowing users to build
their own front-ends for working with our tree-based system.

@@

The tree responses are generated as a single object. This object is the root
node of the tree, and may contain a list of children in the ``children'' field.
The full response format for the tree looks like:

@@

The file responses contain only the files that the selected merge or commit
works with. The response is a single object in the form of a tree. This object
is the root of the tree, and represents the current merge or commit. If the
current position in the tree is an inner node, the response will contain the
child nodes in the ``children'' field, otherwise ``children'' will be null. The
full response format for the file response looks like:
